---
title: "How to {dplyr}"
author: "Lennart Oelschl&auml;ger"
date: 'Last rendered on `r format(Sys.Date(),"%d.%m.%Y")`'
output: slidy_presentation
---
  
## Why and what 

Welcome to this tiny course on data manipulation in R with [{dplyr}](https://dplyr.tidyverse.org/)! `r emo::ji("wave")`

### Why do we care?

### Why {dplyr}?

### What is this course about?

### What do you need?

Basic R skills + a not-too-old version of R + RStudio

### At the end of the day...

### My sources

### Found mistakes? Have suggestions?

I'm sure you have! Please leave a note [here](https://github.com/loelschlaeger/howtodplyr/issues/new/choose). `r emo::ji("wish")`

## First steps

Load {dplyr}.

```{r}
# install.packages(dplyr)
library(dplyr)
```

## It's your turn

This course includes tutorials! `r emo::ji("sunglasses")`

Executing the following lines gives you access to the course material:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("loelschlaeger/howtodplyr")
library(howtodplyr)
```

To start the tutorial, type:

```{r, eval = FALSE}
tutorial()
```

To open a copy of these slides, type:

```{r, eval = FALSE}
slides()
```

To submit an issue on GitHub about this course, type:

```{r, eval = FALSE}
issue()
```
